Stimjim: open source hardware for precise electrical stimulation

### 2019-05-12 benchmarking/paper/draft2.Rnw
got pulse widths calibrated right.

cl = makeCluster(detectCores()-1)
res = parLapply(cl, dataFiles, getPulseParams, fs=fs, vpau=vpau)
res = unlist(res, recursive = FALSE)
stopCluster(cl)
@

@@

\begin{table}
\small{
\begin{tabular}{|l|c|c|c|c|}
\hline
                                & Stimjim     & PulsePal     & STG400x (Multichannel Systems)    & PHM-15x (Med associates) \\
\hline
 Number of output channels      & 2           & 4            &  2-8                              & 2                        \\
 Current output mode            & X           &              &  X                                & X                        \\
 Voltage output mode            & X           & X            &  X                                &                          \\
 Outputs are electrically isolated           & X           &              &  X                                & X                        \\
 Onboard measurement            & X           &              &                                   & Optional                 \\
 Compliance voltage             & $\pm$ 13.7V & $\pm$ 15V    & $\pm$ 120V                        & $\pm$ 45V                \\
 Fastest pulse                  & 50us        & 10us         & 20us                              & 60us                     \\
 Cost (USD)                     & \$194       & \$200        & \$4131 (2 channels)               &  \$6211 (plus \$4438     \\
                                &             &              & \$7462  (4 channels)              &  for necessary software) \\
                                &             &              & \$10327 (8 channels)              &                          \\
 Open source                    & X           & X            &                                   &                          \\
 \hline
\end{tabular}
}
\caption{\label{tab:stimulatorComparison} Comparison of Stimjim vs other related hardware. Cost was obtained as either the complete cost of the bill of materials (Stimjim and PulsePal) or quoted prices from manufacturers (STG400x and PHM-15x).}
\end{table}

@@

ex3 = sapply(dataFiles[seq(81,61,length.out=6)], function(f){
  dat = matrix(readBin(f, what='integer', n=1e7, size=2, endian = 'big'),ncol=2,byrow=TRUE)
  fp = min(which(dat[,1] > 10))
  dat[fp + (-300:700),1]*vpau
})

>>>>

cl = makeCluster(detectCores()-1)
res = parLapply(cl, dataFiles, getPulseParams, fs=fs, vpau=vpau)
#res = list(); for (i in 1:length(dataFiles)) res[[i]] = getPulseParams(dataFiles[i], fs=fs, vpau=vpau)

res = unlist(res, recursive = FALSE)
stopCluster(cl)
@

@@

\begin{table}
\small{
\begin{tabular}{|l|c|c|c|c|c|}
\hline
                                &             &              & STG400x                           & PHM-15x                  &  \\
                                & Stimjim     & PulsePal     & (Multichannel Systems)            & (Med associates)         & ISO-O1B (NPI) \\
\hline
 Number of output channels      & 2           & 4            &  2-8                              & 2                        & 1             \\ 
 Stimulus generator included?   & X           & X            &  X                                & X                        &               \\  
 Current output mode            & X           &              &  X                                & X                        & X                        \\
 Voltage output mode            & X           & X            &  X                                &                          & X                        \\
 Outputs electrically isolated  & X           &              &  X                                & X                        & X                        \\
 Onboard measurement            & X           &              &                                   & Optional                 & X (compliance warning)   \\
 Compliance voltage             & $\pm$ 13.7V & $\pm$ 15V    & $\pm$ 120V                        & $\pm$ 45V                & $\pm$ 100V     \\
 Fastest pulse                  & 50us        & 10us         & 20us                              & 60us                     & 10us           \\
 Cost (USD)                     & \$194       & \$200        & \$4131 (2 channels)               &  \$6211 (plus \$4438     & \$1708         \\
                                &             &              & \$7462  (4 channels)              &  for necessary software) &                \\
                                &             &              & \$10327 (8 channels)              &                          &                \\
 Open source                    & X           & X            &                                   &                          &                \\
 \hline
\end{tabular}
}
\caption{\label{tab:stimulatorComparison} Comparison of Stimjim vs other related hardware. Cost was obtained as either the complete cost of the bill of materials (Stimjim and PulsePal) or quoted prices from manufacturers (STG400x and PHM-15x).}
\end{table}

@@

ex3 = sapply(dataFiles[seq(81,61,length.out=6)], function(f){
  dat = matrix(readBin(f, what='integer', n=1e7, size=2, endian = 'big'),ncol=2,byrow=TRUE)
  fp = min(which(dat[,1] > 10))
  dat[fp + (-200:700),1]*vpau
})
